\documentclass[10pt]{letter}
\usepackage{fontawesome}
\usepackage{hyperref}

% Margins
\topmargin=-1in % Moves the top of the document 1 inch above the default
\textheight=8.5in % Total height of the text on the page before text goes on to the next page, this can be increased in a longer letter
\oddsidemargin=-10pt % Position of the left margin, can be negative or positive if you want more or less room
\textwidth=6.5in % Total width of the text, increase this if the left margin was decreased and vice-versa
%\let\raggedleft\raggedright % Pushes the date (at the top) to the left, comment this line to have the date on the right

\begin{document}
%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------
\begin{letter}{Dr. Richard White \\
Chief Editor of Scientific Reports \\
Springer Nature Limited \\
The Campus, 4 Crinan Street\\
London, N1 9XW \\
UK
} 

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------
\begin{flushright}
\large\bf Miguel Xochicale \\ % Your name
%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
4th Floor \\
Lambeth Wing  St. Thomas' Hospital \\
Westminster Bridge Road \\
London SE1 7EH \\
\faEnvelopeO  miguel.xochicale@kcl.ac.uk \\
\faMobile  (+44) 0744 281 7616 \\
\faHome \href{http://mxochicale.github.io}{http://mxochicale.github.io}
%\vspace{20pt}
%\large\bf Chris Baber, Professor \\ % Your name
%%\vspace{20pt} \hrule height 1pt % If you would like a horizontal line separating the name from the address, uncomment the line to the left of this text
%123 Broadway \\ City, State 12345 \\ (000) 111-1111 % Your address and phone number
\end{flushright} 

%\vfill
\vspace{20pt}
%\author{Miguel Xochicale, King's College London}
\signature{Miguel Xochicale} % Your name for the signature at the bottom

%----------------------------------------------------------------------------------------
%	LETTER CONTENT SECTION
%----------------------------------------------------------------------------------------

\opening{Dear Editor Richard White,}

%* The affiliation and contact information of your corresponding author
I have the pleasure of sending you the manuscript entitled 
"Nonlinear methods to quantify Movement Variability in Human-Humanoid Interaction Activities"
authored by Miguel Xochicale and Chris Baber to be considered for publication as a research article 
in your prestigious journal Scientific Reports.

%* A brief explanation of why the work is appropriate for Scientific Reports
We selected Scientific Reports for 
its reputation on publishing works that are algigment to the principles of reproducibility and open science. 
as well as the various topics and readers in areas of natural and clinical science that our work can be reached. 
Paper is containing original research and has not been submitted or published earlier 
in any journal and is not being considered for publication elsewhere. 
All authors have seen and approved the manuscript and have contributed significantly for the paper.

%* The names and contact information of any reviewers you consider suitable
%* The names of any referees you would like excluded from reviewing
Two potential reviewers that we consider suitable for our work can be:
Bedartha Goswami, bedartha.goswami@uni-tuebingen.de,
at University of Tübingen investigating nonlinear time series analysis; recurrence plots, and
Serhiy Yanchuk, yanchuk@math.tu-berlin.de, at Technical University of Berlin investigating 
dynamics time delay networks of dynamical systems; pattern formation; coupled systems.


%BLURS
%The manuscript is original (i.e., my co-author and myself wrote it, not copied it).
%https://www.aje.com/en/arc/writing-cover-letter/

\closing{Sincerely yours,}

\encl{manuscript and supplementary document} 
% List your enclosed documents here, comment this out to get rid of the "encl:"
%----------------------------------------------------------------------------------------

\end{letter}
\end{document}
